Draft Figures: 12.23.18

### 2018-12-23 draft_figures_12.23.18.Rmd
catch calcuations fixed, and new mpa graphs

---
title: "draft_figures_12.18.18"
author: "Juliette Verstaen"
date: "12/18/2018"
output: pdf_document
toc: true
toc_depth: 2
---

@@

suppressPackageStartupMessages({
  library(tidyverse)
  library(tidyr)
  library(here)
  library(ggplot2)
  library(dplyr)
  library(readxl)
  library(devtools)
  library(plotly)
  library(base)
  library(rio)
  library(plyr)
})
```

@@

@@

LOOK AT THIS TOMORROW. ITQ AND NO ITQ CATCH PROJECTIONS SHOULD BE THE SAME, USING SAME DATA, BUT THEY ARE NOT. WTF?

##Total Catches in most recent year of ITQ, no ITQ, and Turfs
```{r}

@@

fisheries_rightsbased <- fisheries_recent %>%
  mutate(rightsbased = case_when(
    turf == TRUE ~ "2",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0",
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1"
    ))

turfs <- filter(fisheries_rightsbased, rightsbased == "2")
itq <- filter(fisheries_rightsbased, rightsbased == "1")
no_itq <- filter(fisheries_rightsbased, rightsbased == "0")

sum(turfs$Catch, na.rm = TRUE)
#174065.5

sum(itq$Catch, na.rm = TRUE)
#3874741

sum(no_itq$Catch, na.rm = TRUE)
#66155763

@@

## Total Catch: A more generous estimation of Turf catch
```{r}

#load in data for turf/itq only projection
turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")

turf_only <- turf_itq_isscaap %>%
  select(SciName, Country, turf)

@@

#merge the most recent data on each fishery with turf data
fisheries_recent_generousturf <- merge(fisheries_recent_generousturf_1,turf_only, by = c("Country", "SciName") , all.x = "TRUE")

@@

#create dfs for turf, itq, and no itq fisheries to calculate the sum of each
#NOTE to rememeber: the data from these fisheries are the most recent numbers we have. they are not all in the same year 
turfs_generous <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "2")
itq_generous <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "1")
no_itq_generous <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "0")

sum(turfs_generous$Catch, na.rm = TRUE)
#1530353

sum(itq_generous$Catch, na.rm = TRUE)
#8374634

sum(no_itq_generous$Catch, na.rm = TRUE)
#69025946

@@

turf = 1,530,353 -> 1.93% global catch
itq= 8,374,634 -> 10.6% global catch
no itq =  69,025,946 -> 87.46% global catch

Total: 78,930,933

*note: 5643 actual rows
5707 when manually added added
- this means 64 species were matched with existing species in database
- when separated out all by species it was worse
- separate remaining by genus?

@@

new UN GDP data, 2016 only
Scaled GDPs
Rerun Regressions
###itq or turf: probablity of itq = f(ISSCAPP and GDP)

@@

turf_only <- turf_itq_isscaap %>%
  select(SciName, Country, turf, SpeciesCat)

@@

fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")

@@

##Larger Categories for ISSCAAP Codes
11,13 = freshwater fish = 1
22-24 = diadromous fishes = 2
31-35, 37 = marine fishes = 3
42-45,47 = crustaceans = 4
52-58 = molluscs = 5
74,76,77 = miscellaneous aquatic animals = 7

@@

fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName", "SpeciesCat"), all = "TRUE")

@@

Run Turf versus ITQ probably: prob(ITQ). Turf = 1 and ITQ = 0 with the data set that was the turf/itq only one
```{r}
fisheries_recent <- read_csv("data/fisheries_recent.csv")

@@

fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")

@@

##Larger Categories for ISSCAAP Codes
11,13 = freshwater fish = 1
22-24 = diadromous fishes = 2
31-35, 37 = marine fishes = 3
42-45,47 = crustaceans = 4
52-58 = molluscs = 5
74,76,77 = miscellaneous aquatic animals = 7

@@

###MPA New Costello Data
These MPAs are at least partitally no-take but some of the percentages are very low

@@

>>>>

---
title: "Draft Figures: 12.23.18"
author: "Juliette Verstaen"
date: "12/18/2018"
output: pdf_document
toc: true
toc_depth: 2
---

@@

suppressPackageStartupMessages({
  library(tidyverse)
  library(tidyr)
  library(here)
  library(ggplot2)
  library(dplyr)
  library(readxl)
  library(devtools)
  library(plotly)
  library(base)
  library(rio)
  library(plyr)
  library(knitr)
})
```

@@

```{r message=FALSE}

@@

##Total Catch: Most recent year for each fishery 
```{r}

@@

fisheries_turf_itqs <- fisheries_recent %>%
  mutate(rightsbased = case_when(
    turf == TRUE ~ "2",
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"
    ))

turfs_catch <- filter(fisheries_turf_itqs, rightsbased == "2")
itq_catch <- filter(fisheries_turf_itqs, rightsbased == "1")
no_itq_catch <- filter(fisheries_turf_itqs, rightsbased == "0")

sum(turfs_catch$Catch, na.rm = TRUE)

sum(itq_catch$Catch, na.rm = TRUE)

sum(no_itq_catch$Catch, na.rm = TRUE)

@@

## Total Catch: A more generous estimation of Turf catch

```{r message =FALSE}

#load data with info only on most recent year for each fishery (includes upside, updated with RAMs, corbette itq/turf data)
fisheries_recent <- read_csv("data/fisheries_recent.csv")

#turf data from edf and discover turfs
turfs_edf_dt <- read_csv("data/turfs_edf_dt.csv")
```

@@

#merge the most recent data on each fishery with turf data
fisheries_recent_generousturf <- merge(fisheries_recent_generousturf_1, turfs_edf_dt, by = c("Country", "SciName") , all.x = "TRUE")

@@

#create dfs for turf, itq, and no itq fisheries to calculate the sum of each
#NOTE to rememeber: the data from these fisheries are the most recent numbers we have. they are not all in the same year

turfs_generous <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "2")
itq_generous <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "1")
no_itq_generous <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "0")

sum(turfs_generous$Catch, na.rm = TRUE)

sum(itq_generous$Catch, na.rm = TRUE)

sum(no_itq_generous$Catch, na.rm = TRUE)

@@

turf = 1,643,571 -> 2.3% global catch
itq= 3,874,741 -> 5.5% global catch
no itq =  64,815,841 -> 92.1% global catch

Total: 70,334,153

@@

- new UN GDP data, 2016 only
- Scaled GDPs

###Probablity of itq = f(ISSCAPP and GDP)

@@

@@

colnames(fisheries_recent_generousturf_1) <- c("Country", "assess_id_short", "Year", "CommName", "Biomass", "Catch", "BvBmsy", "FvFmsy", "Dbase", "SciName", "IdLevel", "SpeciesCat", "Profits", "MSY", "Price", "g", "k", "c", "phi", "itq", "ivq", "iq")
fisheries_recent_generousturf <- merge(fisheries_recent_generousturf_1, turfs_edf_dt, by = c("Country", "SciName") , all.x = "TRUE")

@@

**The intercepts for the species categories are not coming up as significant at all. Recategorized fish according to the next level up for the ISSCAAP codes. Reclassifications are below: **

Larger Categories for ISSCAAP Codes
11,13 = freshwater fish = 1
22-24 = diadromous fishes = 2
31-35, 37 = marine fishes = 3
42-45,47 = crustaceans = 4
52-58 = molluscs = 5
74,76,77 = miscellaneous aquatic animals = 7

###Rerun Logits with higher up species categories
```{r}

@@

fisheries_recent_generousturf <- merge(fisheries_recent_generousturf_1, turfs_edf_dt, by = c("Country", "SciName") , all.x = "TRUE")

@@

```
Larger categories do not seem to make a difference

###Run Turf versus ITQ probably: prob(ITQ). Turf = 1 and ITQ = 0 with the data set that was the turf/itq only one
```{r}

@@

fisheries_recent_generousturf <- merge(fisheries_recent_generousturf_1, turfs_edf_dt, by = c("Country", "SciName") , all.x = "TRUE")

@@

**The intercepts for the species categories are not coming up as significant at all. Recategorized fish according to the next level up for the ISSCAAP codes. Reclassifications are below: **

Larger Categories for ISSCAAP Codes
11,13 = freshwater fish = 1
22-24 = diadromous fishes = 2
31-35, 37 = marine fishes = 3
42-45,47 = crustaceans = 4
52-58 = molluscs = 5
74,76,77 = miscellaneous aquatic animals = 7

###Rerun Logits with higher up species categories

@@

##MPA New Costello Data

These MPAs are at least partitally no-take but some of the percentages are very low

@@

##Estimates of lost global economic value from lack of managemnet

**1. Costello et al 2016 **
2050

-	RBFM policy applied to just stocks of conservation concern = $31 billion in fisheries profit

-	RBFM policy applied to all stocks = $53 billion in fisheries profit

**2. Original Sunken Billions (2009)**

- “current annual net benefits from marine capture fisheries are tens of billions of U.S. dollars less than the potential benefits”
```{r}
include_graphics("sunkenbillionstable.png")
```

**3. Updated Sunken Billions (2012)**

-	economic losses of about $83 billion
